Manuscript

### 2015-03-10 inst/simulation/manuscript.Rmd
...

```{r figure-4-init}
getPopulationCorrelations <- function(scenarios, modelNames, cutoff=Inf) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=cutoff)
  populationCorrelations <- validation$getValidationSpatialPopulationSizes(scenarios=scenarios, modelNames=modelNames)
  return(populationCorrelations)
}

>>>>

```{r figure-x-debug}
getTrueAndEstimatedCounts <- function(scenarios, modelNames, cutoff=c(-Inf,Inf)) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=cutoff)
  counts <- validation$getCounts(scenarios=scenarios, modelNames=modelNames)
  counts <- ddply(counts, .(iteration), function(x) data.frame(Scenario=x$Scenario[1], Model=x$Model[1], True=mean(x$True), TrueSD=sd(x$True), Estimated=mean(x$Estimated), EstimatedSD=sd(x$Estimated)))
  return(counts)
}

c1 <- getTrueAndEstimatedCounts(scenarios=scenarios, modelNames=modelNames[c(1,3:5)])
c2 <- getTrueAndEstimatedCounts(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[c(1,3:5)])
c3 <- getTrueAndEstimatedCounts(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[c(1,3:5)])

```{r figure-4-init}
getPopulationCorrelations <- function(scenarios, modelNames, cutoff=c(-Inf,Inf)) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeOverEstimate=cutoff)
  populationCorrelations <- validation$getValidationSpatialPopulationSizes(scenarios=scenarios, modelNames=modelNames)
  return(populationCorrelations)
}
